Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-08-27 Documents/Paper/ms.tex
Editing in N proposal section

We will assume that the prior for $N$ is a discrete uniform distribution
between 0 and some $N_{\rm max}$, inclusive. The proposal starts by choosing
a new value $N'$ according to
\begin{eqnarray}
N' &=& \textnormal{mod}\left(N + \delta_N, N_{\rm max} + 1\right)
\end{eqnarray}
where $\delta_N$ is drawn from a heavy tailed
distribution. The most probable values of $\delta_N$ are $\pm 1$, but values
of order $N_{\rm max}$ also have some probability, to allow fast exploration
when the target distribution is similar to the prior.

If $N' > N$, the extra parameters needed, $\{\xx_i\}_{i=N+1}^{N'}$,
are drawn from their prior conditional on the current value of the
hyperparameters, i.e. the interim prior $p(\xx | \hyperparams)$.

If $N' < N$, then $N - N'$ objects must be removed from the model. All
of the objects have the same probability of being selected for removal.

>>>>

We will assume that the prior for $N$ is a discrete uniform distribution
between 0 and some $N_{\rm max}$, inclusive. The proposal starts by choosing
a new value $N'$ according to
\begin{eqnarray}
N' &=& \textnormal{mod}\left(N + \delta_N, N_{\rm max} + 1\right)
\end{eqnarray}
where $\delta_N$ is drawn from a heavy tailed
distribution which is a discrete analogue of Equation~\ref{eqn:heavytailed}.
The most probable values of $\delta_N$ are $\pm 1$, but values
of order $N_{\rm max}$ also have some probability, to allow fast exploration
when the target distribution is similar to the prior. If $N' = N$, $N'$ is
regenerated as $N+1$ with probability 0.5, and $N-1$ with probability 0.5,
and then wrapped back into the range $\{0,...,N_{\rm max}\}$ if necessary.

If $N' > N$, i.e. the proposal is to add objects to the model,
the extra parameters needed, $\{\xx_i\}_{i=N+1}^{N'}$,
are drawn from their prior conditional on the current value of the
hyperparameters, i.e. the interim prior $p(\xx | \hyperparams)$.

If $N' < N$, i.e. the proposal is to remove objects from the model,
then $N - N'$ objects must be selected for removal. All
of the objects have the same probability of being selected for removal.
